%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Rohan}{Pithadiya}{
\href{mailto:rohan.pithadia@gmail.com}{rohan.pithadia@gmail.com} | +91-8007713733 | Hyderabad-India
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     BRIEF
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{2mm}
\descript{\textbf{BRIEF:} 7.5 Years of work experience, post graduation in computer science from IIT Kharagpur, worked on languages like python , c, c++, distributed systems, web technologies, opensource technology enthusiast.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IIT Kharagpur}
\descript{MTech in Computer Science}
\location{Batch 2009}
\sectionsep

\subsection{Nirma Institute}
\descript{BE in Information Technology}
\location{Batch 2005}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Programming}
C \textbullet{} C++  \textbullet{}  Python  \textbullet{} JavaScript
\vspace{2mm} 

\subsection{Concepts}
Distributed System \textbullet{} Web Technologies \textbullet{} Data Structure \textbullet{} Algorithm
\vspace{2mm} 

\subsection{OpenSource Technologies}
Kafka \textbullet{} StreamSets  \textbullet{}  ZooKeeper  \textbullet{} RabbitMQ \textbullet{} Airflow
\vspace{2mm} 

\subsection{Web Technologies}
Web Services \textbullet{} REST  \textbullet{} 3rd Party API integration \textbullet{} Micro Services  \textbullet{} AWS
\vspace{2mm} 

\subsection{UnitTest \& Deployments}
pyTest \textbullet{} unittest  \textbullet{}  docker 
\vspace{2mm} 

\subsection{Database and DataStore}
Postgres \textbullet{} MySQL  \textbullet{}  MongoDB  \textbullet{} Redis

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience} 
\subsection{3loq Labs}
Oct 2017 – Present \textbullet{} SSE
\vspace{2mm} 

\subsection{Culture Machine Media}
July 2015 – Oct 2017 \textbullet{} SSE
\vspace{2mm} 

\subsection{Samsung Research India}
April 2012 – March 2015 \textbullet{} SSE
\vspace{2mm} 

\subsection{Max Secure Software}
February 2011 – July 2011 \textbullet{} SSE
\vspace{2mm} 

\subsection{GamCom IT Services Ltd.}
December 2009 – February 2011 \textbullet{} SE
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
LinkedIn://  \href{https://www.linkedin.com/in/rohan-pithadiya}{\custombold{RohanPithadiya}} \\
Github:// \href{https://github.com/Rohanpithadiya}{\custombold{RohanPithadiya}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Habitual-AI}
\descript{| 3loq labs }
\location{}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Habitual-AI is a habit building recommendation system.
\item Currently building this product from inception to production.
\item Developed the data pipeline-data ingestion to recommendation.
\item Created SAAS based platform for Insights \& Analytics.
\end{tightemize}
\sectionsep

\runsubsection{Video Machine}
% \descript{| Software Engineering Intern }
\descript{| culture machine media }
\location{}
\begin{tightemize}
\item  SaaS application which automatically generate videos at scale.
\item Built a priority mechanism for video generation which reduces video turnaround time from a few hours to approx 10 minutes.
\item Built an image suggestion system, helps reduced time to curate video for production team.
\item Built an asset importer which imports assets from stock services such as Reuters, Shutterstock, Getty to improve quality of videos.
\end{tightemize}
\sectionsep

\runsubsection{SmartHub On Cloud}
\descript{| samsung }
\location{}
\begin{tightemize}
\item Platform streams server based applications to low end devices(TV, Mobiles).
\item Supported games and applications like Fifa, MsOffice, Firefox.
\item Worked on supporting TV(linux) and mobile(android) on same data channel.
\item Worked on load balancing of application servers to distribute load.
\end{tightemize}
\sectionsep

\runsubsection{Traffic Redundancy Elimination (TRE)}
\descript{| samsung }
\location{}
\begin{tightemize}
\item The project was about reducing latency and server overhead while transferring data over network.
\item Worked on dynamically dividing chunks using fingerprint algorithm to identify data change.
\item Worked on receiver to transfer data using TRE approach.
\end{tightemize}
\sectionsep

\runsubsection{PDF-AnitVirus Tool}
\descript{| MaxSecure }
\location{}
\begin{tightemize}
\item The tool scans PDFs for viruses(malicious codes) and quarantines them.
\item No 3rd party library used, developed from scratch.
\item Achieved 93\% accuracy in test data set.
\end{tightemize}
\sectionsep

\runsubsection{Anti Spam Plugin for Outlook}
\descript{| MaxSecure }
\location{}
\begin{tightemize}
\item Developed plugin to classify incoming mail to spam or not, using Naive Bayes classifier algorithm.  It also learned from blacklisted mails and keywords.
\end{tightemize}
\sectionsep

\section{ACADEMIC PROJECTS}
\runsubsection{Reduce Energy Consumption for Task Scheduling in Hard Real-Time System}
\descript{| master thesis }
\location{}
\begin{tightemize}
\item Achieved 47\% - 50\% energy reduction in average workload.  
\end{tightemize}
\sectionsep

\runsubsection{Automation of License Plate Recognition}
\begin{tightemize}
\item Achieved 96\% accuracy in character recognition using NN while 82\% in plate detection.
\end{tightemize}
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}